Scientific Reports Title to see here (20 words or less)

### 2016-08-31 draft1.tex
Added results about allowing k2 and beta to vary during optimization

$k_2$ and $\beta$ were held constant as to reduce the search space, as done by Olufsen and Ottesen. $\alpha$, the parameter used to smooth the pressure data was held constant at 1.5 to smooth the data with a minimal phase shift. The maximum firing rate, $M$, was held constant, as it only appears in this system of equations by normalizing $n$. The sympathetic nervous system delay, $\tau_d$, was held constant, owing to the propagation of discontinuities. \cite{baker1997pitfalls}

>>>>

$k_2$ and $\beta$ were held constant as to reduce the search space, as done by Olufsen and Ottesen. Additionally, when they were allowed to vary during the optimization, the parameter set generated had very small values for $m_{ach}$ and $m__{nor}$, resulting in a predicted heart rate that was basically constant at $h_0$. While this set of the parameters did mimimize the MSE, it did not capture the intrinsic varation in heart rate. $\alpha$, the parameter used to smooth the pressure data was held constant at 1.5 to smooth the data with a minimal phase shift. The maximum firing rate, $M$, was held constant, as it only appears in this system of equations by normalizing $n$. The sympathetic nervous system delay, $\tau_d$, was held constant, owing to the propagation of discontinuities. \cite{baker1997pitfalls}
